---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## 1 Loading and preprocessing the data

```{r, echo= TRUE}
activity_raw <- read.table(unz("activity.zip", "activity.csv"), header = TRUE, sep = "," ,
                  stringsAsFactors = FALSE)
activity_raw$date <- as.Date(activity_raw$date)
```

## 2 Histogram of the total number of steps taken each day

```{r, echo= TRUE}
activity_sum <- aggregate(steps ~ date, activity_raw, sum, na.rm=TRUE)
hist(activity_sum$steps, main = "Sum steps each day", xlab="Number of steps", col = "blue")
```

## 3 Mean and median number of steps taken each day

```{r, echo= TRUE, message = FALSE, warnings = FALSE}
steps_mean <- mean(activity_sum$steps)
steps_median <- median(activity_sum$steps)
```

The mean of the steps (without missing values) is `r steps_mean`
The median of the steps (without missing values) is `r steps_median`

## 4 Time series plot of the average number of steps taken

```{r, echo= TRUE}
activity_mean <- aggregate(steps ~ interval, activity_raw, mean, na.rm = TRUE)
plot(activity_mean, type = "l", main="Mean of Steps through time", col="blue")
```

## 5 The 5-minute interval that, on average, contains the maximum number of steps


## 6 Code to describe and show a strategy for imputing missing data


## 7 Histogram of the total number of steps taken each day after missing values are imputed


## 8 Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends


